\chapter*{General Conclusion And Perspective}
\addcontentsline{toc}{chapter}{General Conclusion And Perspective}
During this internship, we embarked on a journey of significant learning experiences. We began by understanding the project context and identifying our system's diverse requirements. Through collaborative team discussions, we meticulously planned our work schedule, prioritizing our needs accordingly.

Our final project focused on designing and developing a solution tailored for managing an association. This manuscript comprehensively details each step taken to achieve our anticipated results. Adopting the Scrum methodology, we incrementally built our application, ensuring iterative progress.

Today, the application stands ready for use, successfully meeting our set objectives. Engaging with the research community allowed us to advance across various domains, particularly in development.

We are pleased with the achievements during this internship, having fulfilled all major goals. Our exposure to Scrum methodology and Python programming with Odoo has been invaluable.

Looking ahead, our journey continues as we aim to expand the application's capabilities, including the addition of reporting functionalities. Furthermore, our next step involves developing a website to integrate e-commerce functionalities seamlessly.

In conclusion, this internship provided a platform to apply academic, professional, and interpersonal skills to an engaging topic. We have gained valuable insights into enterprise development, laying a solid foundation for future endeavors.

